% Start a document with the here given default font size and paper size.
\documentclass[10pt,letterpaper]{article}

% Set the page margins.
\usepackage[letterpaper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Alexis Vanier}{}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:alexis.at.amonoid.io}{alexis\mbox{}@\mbox{}amonoid.io}\sbull
\textsmaller{+}1 (514) 730-2459\sbull
\href{https://github.com/avanier}{github.com/avanier}\sbull
\href{https://www.linkedin.com/in/alexis-vanier-94705463}{linkedin.com/in/alexis-vanier-94705463}
\\
Montréal\sbull
Canada

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-0.5em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{A quirky and dynamic tech explorer who draws from his eclectic background and his desire to learn from and about others.}
\\

I'm driven by a need to understand people, how they work, and how they relate to their tools. This apprach allows you to see how processes are just a way to iterate on how people come together around tools, goals and constraints.

I enjoy sharing the discoveries I make, finding the wisdom to be found in defeats, how unexpected parts of others complete a picture too big to see.

I thrive in challenges, both mundane and spectacular.
\end{multicols}


\spacedhrule{0em}{0em}

\roottitle{Experience}

\vspace{0.5em}  % some vertical spacing
\headedsection
  {\href{https://www.lightspeedhq.com}{Lightspeed}}
  {\textsc{Montréal, Canada}} {%
  \headedsubsection
    {DevOps Developer}
    {Aug \apo16 -- present}
    {\bodytext{Lightspeed provides solutions to retailers and restaurants with \acr{Point of Sale} and \acr{eCommerce} solutions, both in the cloud and on-premises. Lightspeed deals with rapid growth, reacts switfly to changes in market, and pounces on opportunities.}}
  \vspace{0.5em}
  \headedsubsection {Challenges} {} {
    \bodytext{
      \bull Participate with backend development teams designing new services\\
      \bull Deployed and integrated a \acr{CI/CD} pipeline system with \href{https://concourse.ci/}{Concourse} across multiple teams and products\\
      \bull Evangelized teams to the to the use of \acr{Docker} and \acr{CI/CD} through presentation, workshops and coaching\\
      \bull Uniformize DevOps practices and infrastructure tools across different products\\
      \bull Transition services running in full VMs under Chef management to Kubernetes\\
      \bull Participate in auditing and hardening infrastructure and services within a payments driven environment}
  }
  \vspace{0.5em}
  \headedsubsection {Technologies} {} {
    \bodytext{\acr{AWS, GCE, GKE, Kubernetes, Concourse, Chef, Ruby, PHP, Git, Jira, SparkleFormation, Terraform, Github, OneLogin, Golang, Java, DataDog, NewRelic, ElasticSearch, Kibana, MySQL, Memcached, Redis, RDS, ElasticBeanstalk, Vault, CentOS, Ubuntu, Docker, Rundeck, Samson}}
  }
}

\vspace{1em}
\headedsection
  {\href{https://www.nuglif.com}{Nuglif}}
  {\textsc{Montréal, Canada}} {%
  \headedsubsection
    {Systems Administrator}
    {Nov \apo15 -- Aug \apo16}
    {\bodytext{Nuglif offers the daily news industry a powerful platform adapted to the needs of today's readers, editors, and advertisers. I was tasked with supporting several backend development teams and ensuring on-call duty on the publication and advertisement services for two newspapers.}}
    \vspace{0.5em}
    \headedsubsection {Challenges} {} {
      \bodytext{
        \bull Participated with backend development teams designing and implementing new services\\
        \bull Participated in the continuous improvement of the escalation process}
    }
    \vspace{0.5em}
    \headedsubsection {Technologies} {} {
      \bodytext{\acr{VMWare, Chef, Ruby, PHP, Git, Bitbucket, Fisheye, Crucible, Jira, Gitolite, LDAP, Golang, Bitbucket, Sensu, RabbitMQ, Statsd, MySQL, CentOS, Ubuntu, SLES, Jenkins, GlusterFS}}
    }
  }

\pagebreak
\headedsection
  {\href{https://www.lapresse.ca}{La Presse}}
  {\textsc{Montréal, Canada}} {%
  \headedsubsection
  {Infrastructure Advisor}
  {Jun \apo13 -- Nov \apo15}
  {\bodytext{La Presse is the second greatest circulation French language newspaper in North America. My mandate ranged from integrating a live production video studio, \acr{IT} services automation and providing custom workflow solutions for a newsroom embracing the digital age.}}
  \vspace{0.5em}
  \headedsubsection {Challenges} {} {
    \bodytext{
      \bull Developed and deployed a custom photo asset management solution, encompassing ingestion, approval, metadata editing, archival, and publication, in one of the largest french language newsrooms in North America \ \ \ \emph{\small{(Ask me about it! It's one of my favourite projects!)}}\\
      \bull Completed the integration for a live video production, multi camera, video studio\\
      \bull Provided expertise for the production, and distribution of audiovisual material on mobile and web platforms\\
      \bull Deployed edit suites for use by journalists and support staff\\
      \bull Deployed a custom multicast video system allowing \acr{24/7} monitoring of news networks for the news desk team\\
      \bull Participated in the production of several special events such as national and provincial elections, sports games, and other exceptional news events}
  }
  \vspace{0.5em}
  \headedsubsection {Technologies} {} {
    \bodytext{\acr{VMWare, Chef, Ruby, Git, SANs, Quantum StorNext, Bare Metal Computing, NodeJS, AngularJS, CSS, Javascript, LDAP, Bitbucket, Sensu, CentOS, Baseband Video, AES Formats, FFMPEG, Subtitling, Apple HLS, MPEG-DASH, BS.1770, CALM, ATSC/A85, and a very long list of codecs for broadcast, editing and web delivery}}
  }
}

\vspace{1em}
\headedsection
{\emph{Freelance}}
{\textsc{Multiple Locations}} {%
\headedsubsection
{Colourist / Digital Acquisition Supervisor}
{Jan \apo05 -- Aug \apo16}
{\bodytext{As a film and commercial professional, I advised productions on how to best capture, edit, post-process and finish digitally acquired motion pictures. The scope of my expertise covered both the qualitative and quantitative, the technical, economical, practical, logistical, and creative of any given project. Often productions would seek my services as a colourist during the finishing phase.}}
\vspace{0.5em}
\headedsubsection {Challenges} {} {
  \bodytext{
    \bull Completed more than 60 music videos, commercials, short films, feature films, web series, reality series, experimental films, and corporate videos\\
    \bull Developed an expertise at designing workflows from the camera to the screen, spanning humans and technologies \emph{\small{(\ldots and budgets)}}\\
    \bull Contributed to an Oscar winning short film, and other award-winning productions}
}}

\begin{center}
  \emph{\small Please refer to \href{https://www.linkedin.com/in/alexis-vanier-94705463/}{my LinkedIn profile} for a more complete list of work experience along with recommendations.}
\end{center}

\spacedhrule{-0.2em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Certifications:}
  {\bull ITIL Foundation}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Big fan of Agile methodologies, continuous delivery and functional programming. Enjoys writing \acr{Erlang}, \acr{Elixir}. Strong preference for declarative systems like PlantUML, GraphViz, Markdown, and \LaTeX. Likes to drill down to root causes of human behaviours in technology, likes to analyze decision processes. Strong interest for picking apart data models, and studying how they are accessed. Jira is an automation language for humans. I know Regular Expressions \emph{\small{(\ldots but I'm not good at lookarounds)}}. Strong Linux administration skills, not afraid to dig down to the Kernel, and has fairly deep knowledge of Linux as user stations. I run \acr{Ceph} at home. Tinkered with \acr{Lisp}, \acr{Scheme}, \acr{Haskell}. Fluent user of GPG / PGP. Automate All the Things, everything as code, version control All the Things.}

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {French \emph{(mother tongue)}, English \emph{(full professional proficiency)}, Japanese \emph{(beginner)}.}


\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in no particular order:}
  {art, functional programming, music, photography, sailing, Scotch, security, and \acr{UX}-design.}

\vspace{1em}
\begin{center}
  \emph{\small You can read the source for my resume \href{https://github.com/avanier/latex-resume/blob/master/alexis-vanier-resume.tex}{on GitHub}}.
\end{center}

\end{document}
